Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
contribution list

This article makes the following contributions:
\begin{enumerate}
\item We recast the guided static analysis technique from \citet{DBLP:conf/sas/GopanR07} on the expanded multigraph from \citet{Monniaux_Gonnord_SAS11}, considering entire paths instead of individual transitions, using SMT queries and binary decision diagrams.\label{contr:guided_multigraph} (See \S\ref{sec:guided_multigraph})
\item We improve the technique for obtaining disjunctive invariants from \citet{DBLP:conf/pldi/GulwaniZ10} by replacing the explicit exhaustive enumeration of paths by a sequence of SMT queries.\label{contr:disjunctive} (See \S\ref{sec:disjunctive})
\item We implemented these techniques, in addition to ``classical'' iterations and the original guided static analysis, inside a prototype static analyzer.
This tool uses the LLVM bitcode format \cite{Lattner:2004:LCF:977395.977673,LLVM_langref} as input, which can be produced by compilation from C, C++ and Fortran, enabling it to be run on many real-life programs.
With respect to abstract domains on numerical variables, it uses the APRON library \cite{DBLP:conf/cav/JeannetM09}, which supports a variety of abstract domains from which we can choose with minimal changes to our analyzer.
This article summarizes our implementation decisions for analysis of SSA-form programs.
\item We conducted extensive experiments with this tool, on real-life programs, thus obtaining experimental comparisons between the various combinations of techniques. (\S\ref{sec:experiments})
\end{enumerate}

@@

\subsection{Precision of Abstract Domains}

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{OCT/PKEQ}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF). We used as abstract domains Convex Polyhedra (PK),
Octagons (OCT), intervals (BOX) and linear equalities (PKEQ).}
\label{tab:domain}
\end{table*}

>>>>

This article makes the following contributions:
\begin{enumerate}
\item We recast the guided static analysis technique from \citet{DBLP:conf/sas/GopanR07} on the expanded multigraph from \citet{Monniaux_Gonnord_SAS11}, considering entire paths instead of individual transitions, using SMT queries and binary decision diagrams.\label{contr:guided_multigraph} (See \S\ref{sec:guided_multigraph})
\item We improve the technique for obtaining disjunctive invariants from \citet{DBLP:conf/pldi/GulwaniZ10} by replacing the explicit exhaustive enumeration of paths by a sequence of SMT queries.\label{contr:disjunctive} (See \S\ref{sec:disjunctive})
\item We implemented these techniques, in addition to ``classical'' iterations and the original guided static analysis, inside a prototype static analyzer.
This tool uses the LLVM bitcode format \cite{Lattner:2004:LCF:977395.977673,LLVM_langref} as input, which can be produced by compilation from C, C++ and Fortran, enabling it to be run on many real-life programs.
With respect to abstract domains on numerical variables, it uses the APRON library \cite{DBLP:conf/cav/JeannetM09}, which supports a variety of abstract domains from which we can choose with minimal changes to our analyzer.
Section~\ref{sec:analysis-algorithm} summarizes our implementation decisions for analysis of SSA-form programs.

\item We conducted extensive experiments with this tool, on real-life programs: (i) fixing the abstract domain, varying the iteration technique (\S~\ref{sec:compare_techniques}) (ii) fixing the iteration technique, varying the abstract domain (\S\ref{sec:compare_domains}).
\end{enumerate}

@@

\subsection{Precision of Abstract Domains}
\label{sec:compare_domains}
\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{PK/OCT}}
& \multicolumn{3}{c|}{\textbf{PK/BOX}}
& \multicolumn{3}{c|}{\textbf{OCT/BOX}}
& \multicolumn{3}{c|}{\textbf{PK/PKEQ}}
& \multicolumn{3}{c|}{\textbf{OCT/PKEQ}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table_domain.tex}
\end{tabular}
\end{center}
\caption{Results of the comparison of the various abstract domains, when using
the same technique (G+PF). We used as abstract domains Convex Polyhedra (PK),
Octagons (OCT), intervals (BOX) and linear equalities (PKEQ).}
\label{tab:domain}
\end{table*}
